Open-source landscape for 3D CSEM modelling

### 2020-09-04 manuscript/Manuscript.tex
Updates from Overleaf

\address{
\footnotemark[1]%
TU Delft,
Building 23,
Stevinweg 1 / PO-box 5048,
2628 CN Delft (NL);\\
\footnotemark[2]%
Leibniz Institut für Angewandte Geophysik,
Stilleweg 2,
30655 Hannover (DE);\\
\footnotemark[3]%
Barcelona Supercomputing Center (BSC),
Nexus II Building c/Jordi Girona, 29,
08034 Barcelona (ES);\\
\footnotemark[4]%
University of California Berkeley,
Department of Statistics (USA).\\
E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
\textbf{Keywords}: CSEM, Open-Source, 3D modelling, FV, FE.
}

@@

%%fakesection ===    ABSTRACT    ===
\begin{abstract}
%
Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) used to be only possible for large companies or research consortia. However, this changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
%
Four different open-source 3D CSEM codes are considered in this work, where in all cases at least the user-facing functionality is written in Python. Two codes, \simpeg and \emg3d, use finite volumes, the other two codes, \custem and \petgem, use finite elements. Three different mesh-types are used, simple tensor meshes, unstructured tetrahedral meshes, and octree meshes. Two models are used to compare the codes, a layered background containing three resistive blocks, and Marlim R3D, a complex, real-world, open-source resistivity data.
%
The comparison shows that all four codes are able to compute the model to sufficient precision. The biggest difference between the codes are actually the used mesh types. The required runtime and memory varies greatly between the codes. However, these requirements depend mainly on the underlying solver, and not on the actual CSEM codes.
%
The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further. We hope that these results may be useful for the entire CSEM community, and we invite and encourage the community to make more code, modelling scripts, and results publicly available. For a start, all the scripts to reproduce our shown results are available.
%
\end{abstract}

>>>>

\address{
\footnotemark[1]%
TU Delft,
Building 23,
Stevinweg 1 / PO-box 5048,
2628 CN Delft (NL);\\
\footnotemark[2]%
Leibniz Institut for Applied Geophysics,
Stilleweg 2,
30655 Hannover (DE);\\
\footnotemark[3]%
Barcelona Supercomputing Center (BSC),
Nexus II Building c/Jordi Girona, 29,
08034 Barcelona (ES);\\
\footnotemark[4]%
University of California Berkeley,
Department of Statistics (USA).\\
E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
\textbf{Keywords}: CSEM, Open-Source, 3D modelling, FV, FE.
}

@@

%%fakesection ===    ABSTRACT    ===
\begin{abstract}
%
Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia. However, this changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
%
Four different open-source 3D CSEM codes are considered in this work, where in all cases at least the user-facing functionality is written in Python. Two codes, \simpeg and \emg3d, use finite volumes, the other two codes, \custem and \petgem, use finite elements. Three different mesh-types are used, simple tensor meshes, unstructured tetrahedral meshes, and octree meshes. Two models are used to compare the codes, a layered background containing three resistive blocks, and Marlim R3D, a complex, real-world, open-source resistivity data.
%
The comparison shows that all four codes are able to compute the model to sufficient precision. The biggest difference between the codes are actually the used mesh types. The required runtime and memory varies greatly between the codes. However, these requirements depend mainly on the underlying solver, and not on the actual CSEM codes.
%
The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further. We hope that these results may be useful for the entire CSEM community, and we invite and encourage the community to make more code, modelling scripts, and results publicly available. For a start, all the scripts to reproduce our shown results are available.
%
\end{abstract}
